\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-20 doc/sw-system.tex
Explained new crowd corner plot: stage one only, for clarity.

To investigate the properties of the \sw crowd, as characterised by their
agents, we define the following quantities and plot their distributions in
\Fref{fig:crowd:cornerplot}.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
\StageTwo it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In \StageOne, the mean experience per agent was 29;
in \StageTwo (where the training image frequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gained
per classification (in bits) by that volunteer,  $\skill$, for subjects which
have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
$\skill = 0.0$~bits, while perfect classifiers have $\skill = 1.0$~bit.
All agents start
with $\skill = 0.0$~bits. The skill of  an agent increases as training subjects are
classified, and the agent's estimates of its confusion matrix elements improve.
In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was
0.05~bits.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's
{\it test subject} classification history, a quantity representative of the
total contribution to the project made by that volunteer (see the appendix for
more discussion of this quantity). The classifications of training images
determine the skill, while the classification of test images determines
contribution.  In \StageOne, the mean  contribution per agent was
34.9 bits; in \StageTwo it was 33.5.
%
\item{\noindent\bf ``Information:''} The actual total information $\information$
generated by the agent during the volunteer's classification activity. This
quantity depends on the value of each subject's lens probability when that
subject was presented to the volunteer (simply because information gain is
defined in terms of posterior relative to prior probabilities,
\Aref{appendix:swap}).  Because of this, we expect this quantity to be noisier
than the ``contribution'' defined above.
%
\end{description}

@@

The similarities between \StageOne and 2, suggest that these numbers could be
scaled to estimate the speed of future \SW projects (or at least those following
a similar blind search strategy). For example, the completion time for a \SW
project could be approximated as
\begin{equation}
    \tau \approx 18\,{\rm days} \left(\frac{10^4}{N_p}\right)
                               \left(\frac{N_s}{10^4}\right),
\end{equation}
where $N_s$ is the number of subjects to be classified, and $N_p$ is the number
of volunteers in the crowd.

@@

However, most identification failures (around 60\%) seem to be due to the
random walk problem. Short, random direction steps arise from low skill
classifiers, arising from classifier inexperience (\Sref{sec:results:crowd}).
While improved training will help reduce this effect, it is here
that targeted task assignment could also help improve system performance, by
bringing higher skill volunteers in to the mix. We
advertised \StageTwo of the current project to all registered users; it was
taken up by \StageOne veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
the \StageTwo classification round, only 774 were veterans from \StageOne.
\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
on to \StageTwo skill and contribution.

This figure suggests that there may be some benefit to opening \StageTwo on the
basis of \StageOne agent skill, in order to reduce the noise in the system
generated by new and low skill volunteers in this more difficult
classification stage.  A simple implementation of this would be to switch the
web app to the \StageTwo version when either a certain \StageOne skill (and/or
effort) threshold was passed. Good strategy would probably be to switch back
to \StageOne after some number of \StageTwo classifications (to avoid losing the
high skill users from \StageOne entirely), and also to make it very clear which
stage the classifier was at (since \StageTwo requires more careful attention).
This is something we plan to experiment with in future.

@@

@@

Finally, we comment on the size of the first \SW crowd, and how the system
might be scaled up for future surveys. In \Sref{sec:results:crowd} and
\Tref{tab:crowd:contributions}, the following rough picture emerged for the
\SW crowd in this project:
it consisted of a few $10^4$ volunteers, with a few $10^3$ achieving
considerable skill, and a few $10^2$ having the time to make a significant
contribution. Slightly more quantitively, we might note that  the total skill
of the crowd, computed by summing the skill of all the agents, is a measure of
the effective crowd size, in the sense that a crowd of perfect classifiers
would be of this size. By this measure,the \StageOne crowd was equivalent to a
team of 1470 perfect classifiers, while the \StageTwo crowd was equivalent to a
team of 102 perfect classifiers. With this same crowd, we can see that surveys
providing a few $10^4$ subjects would be completed quickly, if the high
contribution rate of the current crowd were to be repeated.

@@

\item Participation levels were high (over 36,000 volunteers, contributing
classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
that if this can be maintained, visual inspection of tens of thousands of images
can be performed on timescales of a few weeks.

@@

\item The optimal true positive rate (completeness) and false positive rate in
the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
2). This  FPR translates to a purity of 20\%.

>>>>

To investigate the properties of the \sw crowd, as characterised by their
agents, we define the following quantities and plot their one and 2-D marginal
distributions in
\Fref{fig:crowd:cornerplot}. This figure only shows the \StageOne agents for clarity,
but the trends we found the same trends in \StageTwo.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified
by a volunteer. In \StageOne, the mean effort per agent was 263; in the shorter
\StageTwo it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In \StageOne, the mean experience per agent was 29;
in \StageTwo (where the training image frequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gained
per classification (in bits) by that volunteer,  $\skill$, for subjects which
have lens probability 0.5 (\Aref{appendix:swap}). Random classifiers have
$\skill = 0.0$~bits, while perfect classifiers have $\skill = 1.0$~bit.
All agents start
with $\skill = 0.0$~bits. The skill of  an agent increases as training subjects are
classified, and the agent's estimates of its confusion matrix elements improve.
In \StageOne, the mean skill per agent was 0.04 bits; in  \StageTwo it was
0.05~bits.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's
{\it test subject} classification history, a quantity representative of the
total contribution to the project made by that volunteer (see the appendix for
more discussion of this quantity). The classifications of training images
determine the skill, while the classification of test images determines
contribution.  In \StageOne, the mean  contribution per agent was
34.9 bits; in \StageTwo it was 33.5.
%
\item{\noindent\bf ``Information:''} The actual total information $\information$
generated by the agent during the volunteer's classification activity. This
quantity depends on the value of each subject's lens probability when that
subject was presented to the volunteer (simply because information gain is
defined in terms of posterior relative to prior probabilities,
\Aref{appendix:swap}).  Because of this, we expect this quantity to be noisier
than the ``contribution'' defined above.
%
\end{description}

@@

The similarities between \StageOne and 2, suggest that these numbers could be
scaled to estimate the speed of future \SW projects (or at least those following
a similar blind search strategy). For example, the completion time for a \SW
project may be approximated as
\begin{equation}
    \tau \approx 18\,{\rm days} \left(\frac{10^4}{N_p}\right)
                               \left(\frac{N_s}{10^4}\right),
\label{eq:speed}
\end{equation}
where $N_s$ is the number of subjects to be classified, and $N_p$ is the number
of volunteers in the crowd.

@@

However, most identification failures (around 60\%) seem to be due to the
random walk problem. Short, random direction steps arise from low skill
classifiers, arising from classifier inexperience (\Sref{sec:results:crowd}).
While improved training will help reduce this effect, it is here
that targeted task assignment could also help improve system performance, by
bringing higher skill volunteers in to the mix. We
advertised \StageTwo of the current project to all registered users; it was
taken up by \StageOne veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
the \StageTwo classification round, only 774 were veterans from \StageOne.

\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
on to \StageTwo skill and contribution.
This figure suggests that there may be some benefit to opening \StageTwo on the
basis of \StageOne agent skill, in order to reduce the noise in the system
generated by new and low skill volunteers in this more difficult
classification stage.  A simple implementation of this would be to switch the
web app to the \StageTwo version when either a certain \StageOne skill (and/or
effort) threshold was passed. Good strategy would probably be to switch back
to \StageOne after some number of \StageTwo classifications (to avoid losing the
high skill users from \StageOne entirely), and also to make it very clear which
stage the classifier was at (since \StageTwo requires more careful attention).
This is something we plan to experiment with in future.

@@

If the system efficiency could be improved by a factor of three, we would
expect the coefficient in \Eref{eq:speed} to decrease by roughly the same factor,
suggesting that an dataset of $10^4$~images could be searched for lenses by a
crowd of $10^4$ volunteers in about 6 days.

@@

Finally, we comment on the size of the first \SW crowd, and how the system might
be scaled up for future surveys. In \Sref{sec:results:crowd} and
\Tref{tab:crowd:contributions}, the following rough picture emerged for the \SW
crowd in this project: it consisted of a few $10^4$ volunteers, with a few
$10^3$ achieving considerable skill, and a few $10^2$ having the time to make a
significant contribution. Slightly more quantitively, we might note that  the
total skill of the crowd, computed by summing the skill of all the agents, is a
measure of the effective crowd size, in the sense that a crowd of perfect
classifiers would be of this size. By this measure,the \StageOne crowd was
equivalent to a team of 1470 perfect classifiers, while the \StageTwo crowd was
equivalent to a team of 102 perfect classifiers. With this same crowd, we saw in
\Sref{sec:results:speed}  that surveys providing a few $10^4$ subjects would be
completed quickly, if the high contribution rate of the current crowd were to be
repeated.

@@

\item Participation levels were high (over 36,000 volunteers, contributing
classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
that if this can be maintained, visual inspection of tens of thousands of images
could be performed on timescales of weeks.

@@

\item The optimal true positive rate (completeness) and false positive rate in
the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
2). This FPR translates to an approximate purity of 20\%.
